Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber{}}}

### 2018-02-07 Paper.tex
Cleanup ECREC definition and a few other things

\hypertarget{Phi}{}And finally define $\Phi$, the block transition function, which maps an incomplete block $B$ to a complete block $B'$:
\begin{eqnarray}
\Phi(B) & \equiv & B': \quad B' = B^* \quad \text{except:} \\
B'_{\mathrm{n}} & = & n: \quad x \leqslant \frac{2^{256}}{H_{\mathrm{d}}} \\
B'_{\mathrm{m}} & = & m \quad \text{with } (x, m) = \mathtt{PoW}(B^*_{\hcancel{n}}, n, \mathbf{d}) \\
B^* & \equiv & B \quad \text{except:} \quad B^*_{\mathrm{r}} = r(\Pi(\Gamma(B), B))
\end{eqnarray}
With $\mathbf{d}$ being a dataset as specified in appendix \ref{app:ethash}.

@@

\bibliography{Biblio}
\bibliographystyle{plainnat}

@@

For the elliptic curve DSA recover VM execution function, we also define $\mathbf{d}$ to be the input data, well-defined for an infinite length by appending zeroes as required. Importantly in the case of an invalid signature ($\mathtt{\tiny ECDSARECOVER}(h, v, r, s) = \varnothing$), then we have no output.
\begin{eqnarray}
\Xi_{\mathtt{ECREC}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{where:} \\
g_{\mathrm{r}} &=& 3000\\
|\mathbf{o}| &=& \begin{cases} 0 & \text{if} \quad \mathtt{\tiny ECDSARECOVER}(h, v, r, s) = \varnothing\\ 32 & \text{otherwise} \end{cases}\\
\text{if} \quad |\mathbf{o}| = 32: &&\\
\mathbf{o}[0..11] &=& 0 \\
\mathbf{o}[12..31] &=& \mathtt{\tiny KEC}\big(\mathtt{\tiny ECDSARECOVER}(h, v, r, s)\big)[12..31] \quad \text{where:}\\
\mathbf{d}[0..(|I_{\mathbf{d}}|-1)] &=& I_{\mathbf{d}}\\
\mathbf{d}[|I_{\mathbf{d}}|..] &=& (0, 0, ...) \\
h &=& \mathbf{d}[0..31]\\
v &=& \mathbf{d}[32..63]\\
r &=& \mathbf{d}[64..95]\\
s &=& \mathbf{d}[96..127]
\end{eqnarray}

The two hash functions, RIPEMD-160 and SHA2-256 are more trivially defined as an almost pass-through operation. Their gas usage is dependent on the input data size, a factor rounded up to the nearest number of words.
\begin{eqnarray}
\Xi_{\mathtt{SHA256}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{where:} \\
g_{\mathrm{r}} &=& 60 + 12\Big\lceil \dfrac{|I_{\mathbf{d}}|}{32} \Big\rceil\\
\mathbf{o}[0..31] &=& \mathtt{\tiny SHA256}(I_{\mathbf{d}})\\
\Xi_{\mathtt{RIP160}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{where:} \\
g_{\mathrm{r}} &=& 600 + 120\Big\lceil \dfrac{|I_{\mathbf{d}}|}{32} \Big\rceil\\
\mathbf{o}[0..11] &=& 0 \\
\mathbf{o}[12..31] &=& \mathtt{\tiny RIPEMD160}(I_{\mathbf{d}})\\
\end{eqnarray}

For the purposes here, we assume we have well-defined standard cryptographic functions for RIPEMD-160 and SHA2-256 of the form:
\begin{eqnarray}
\mathtt{\small SHA256}(\mathbf{i} \in \mathbb{B}) & \equiv & o \in \mathbb{B}_{32} \\
\mathtt{\small RIPEMD160}(\mathbf{i} \in \mathbb{B}) & \equiv & o \in \mathbb{B}_{20}
\end{eqnarray}

@@

We define a precompiled contract for zkSNARK verification.
\begin{eqnarray}
\Xi_{\mathtt{SNARKV}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\qquad\Xi_{\mathtt{SNARKV}}(\boldsymbol\sigma,g,I)&=&(\varnothing,0,A^0,())\quad\text{if}\ F\\
F&\equiv&(|I_{\mathbf{d}}|\bmod 192\neq 0\vee(\exists j.\ a_{\mathrm{j}}=\varnothing\vee b_{\mathrm{j}}=\varnothing))\\
k &=& \dfrac{|I_{\mathbf{d}}|}{192} \\
g_{\mathrm{r}}&=& 60000k + 40000 \\
\mathbf o[0..31]&\equiv&\begin{cases}
0x0000000000000000000000000000000000000000000000000000000000000001&\text{if}\ v\wedge\neg F\\
0x0000000000000000000000000000000000000000000000000000000000000000&\text{if}\ \neg v\wedge\neg F
\end{cases}\\
v&\equiv&(\log_{P_1}(a_1)\times\log_{P_2}(b_1)+\cdots+\log_{P_1}(a_{\mathrm{k}})\times\log_{P_2}(b_{\mathrm{k}})\equiv 1\mod q)\\
a_1&\equiv&\delta_1(I_{\mathbf d}[0..63])\\
b_1&\equiv&\delta_2(I_{\mathbf d}[64..191])\\\nonumber
\vdots\\
a_{\mathrm{k}}&\equiv&\delta_1(I_{\mathbf d}[(|I_{\mathbf d}|-192)..(|I_{\mathbf d}|-129)])\\
b_{\mathrm{k}}&\equiv&\delta_2(I_{\mathbf d}[(|I_{\mathbf d}|-128)..(|I_{\mathbf d}|-1)])
\end{eqnarray}

We define a precompiled contract for addition on $G_1$.
\begin{eqnarray}
\Xi_{\mathtt{BN\_ADD}}&\equiv&\Xi_{\mathtt{BN\_PRE}}\quad\text{except:}\\
\Xi_{\mathtt{BN\_ADD}}(\boldsymbol\sigma,g,I)&=&(\varnothing,0,A^0,())\quad\text{if}\ x=\varnothing\vee y=\varnothing\\
g_{\mathrm{r}} &=& 500\\
\mathbf o&\equiv&\delta_1^{-1}(x+y)\quad\text{where $+$ is the group operation in $G_1$}\\
x&\equiv&\delta_1(\bar I_{\mathbf d}[0..63])\\
y&\equiv&\delta_1(\bar I_{\mathbf d}[64..127])\\
\label{eq:complemented_input}\bar I_{\mathbf d}[x]&\equiv&\begin{cases}
I_{\mathbf d}[x]&\text{if}\ x < |I_{\mathbf d}|\\
0&\text{otherwise}
\end{cases}
\end{eqnarray}

@@

We assert the functions $\mathtt{\small ECDSASIGN}$, $\mathtt{\small ECDSARECOVER}$ and $\mathtt{\small ECDSAPUBKEY}$. These are formally defined in the literature.
\begin{eqnarray}
\mathtt{\small ECDSAPUBKEY}(p_{\mathrm{r}} \in \mathbb{B}_{32}) & \equiv & p_{\mathrm{u}} \in \mathbb{B}_{64} \\
\linkdest{ECDSASIGN}{}\mathtt{\small ECDSASIGN}(e \in \mathbb{B}_{32}, p_{\mathrm{r}} \in \mathbb{B}_{32}) & \equiv & (v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) \\
\mathtt{\small ECDSARECOVER}(e \in \mathbb{B}_{32}, v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) & \equiv & p_{\mathrm{u}} \in \mathbb{B}_{64}
\end{eqnarray}

>>>>

\hypertarget{Phi}{}And finally define $\Phi$, the block transition function, which maps an incomplete block $B$ to a complete block $B'$:
\begin{eqnarray}
\Phi(B) & \equiv & B': \quad B' = B^* \quad \text{except:} \\
B'_{\mathrm{n}} & = & n: \quad x \leqslant \frac{2^{256}}{H_{\mathrm{d}}} \\
B'_{\mathrm{m}} & = & m \quad \text{with } (x, m) = \mathtt{PoW}(B^*_{\hcancel{n}}, n, \mathbf{d}) \\
B^* & \equiv & B \quad \text{except:} \quad B^*_{\mathrm{r}} = r(\Pi(\Gamma(B), B))
\end{eqnarray}

With $\mathbf{d}$ being a dataset as specified in appendix \ref{app:ethash}.

@@

\bibliographystyle{plainnat}
\bibliography{Biblio}

@@

We define $\Xi_{\mathtt{ERCEC}}$ as a precompiled contract for the elliptic curve digital signature algorithm (ECDSA) public key recovery function (ecrecover). See \ref{app:signing} for the definition of the function $\mathtt{\tiny ECDSARECOVER}$. We also define $\mathbf{d}$ to be the input data, well-defined for an infinite length by appending zeroes as required. In the case of an invalid signature ($\mathtt{\tiny ECDSARECOVER}(h, v, r, s) = \varnothing$), we return no output.

\begin{eqnarray}
\Xi_{\mathtt{ECREC}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{where:} \\
g_{\mathrm{r}} &=& 3000\\
|\mathbf{o}| &=& \begin{cases} 0 & \text{if} \quad \mathtt{\tiny ECDSARECOVER}(h, v, r, s) = \varnothing\\ 32 & \text{otherwise} \end{cases}\\
\text{if} \quad |\mathbf{o}| = 32: &&\\
\mathbf{o}[0..11] &=& 0 \\
\mathbf{o}[12..31] &=& \mathtt{\tiny KEC}\big(\mathtt{\tiny ECDSARECOVER}(h, v, r, s)\big)[12..31] \quad \text{where:}\\
\mathbf{d}[0..(|I_{\mathbf{d}}|-1)] &=& I_{\mathbf{d}}\\
\mathbf{d}[|I_{\mathbf{d}}|..] &=& (0, 0, ...) \\
h &=& \mathbf{d}[0..31]\\
v &=& \mathbf{d}[32..63]\\
r &=& \mathbf{d}[64..95]\\
s &=& \mathbf{d}[96..127]
\end{eqnarray}

We define $\Xi_{\mathtt{SHA256}}$ and $\Xi_{\mathtt{RIP160}}$ as precompiled contracts implementing the SHA2-256 and RIPEMD-160 hash functions respectively. Their gas usage is dependent on the input data size, a factor rounded up to the nearest number of words.

\begin{eqnarray}
\Xi_{\mathtt{SHA256}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{where:} \\
g_{\mathrm{r}} &=& 60 + 12\Big\lceil \dfrac{|I_{\mathbf{d}}|}{32} \Big\rceil\\
\mathbf{o}[0..31] &=& \mathtt{\tiny SHA256}(I_{\mathbf{d}})\\
\Xi_{\mathtt{RIP160}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{where:} \\
g_{\mathrm{r}} &=& 600 + 120\Big\lceil \dfrac{|I_{\mathbf{d}}|}{32} \Big\rceil\\
\mathbf{o}[0..11] &=& 0 \\
\mathbf{o}[12..31] &=& \mathtt{\tiny RIPEMD160}(I_{\mathbf{d}})
\end{eqnarray}

For the purposes here, we assume we have well-defined standard cryptographic functions for RIPEMD-160 and SHA2-256 of the form:

\begin{eqnarray}
\mathtt{\small SHA256}(\mathbf{i} \in \mathbb{B}) & \equiv & o \in \mathbb{B}_{32} \\
\mathtt{\small RIPEMD160}(\mathbf{i} \in \mathbb{B}) & \equiv & o \in \mathbb{B}_{20}
\end{eqnarray}

@@

We define $\Xi_{\mathtt{SNARKV}}$ as a precompiled contract for zkSNARK verification.
\begin{eqnarray}
\Xi_{\mathtt{SNARKV}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\qquad\Xi_{\mathtt{SNARKV}}(\boldsymbol\sigma,g,I)&=&(\varnothing,0,A^0,())\quad\text{if}\ F\\
F&\equiv&(|I_{\mathbf{d}}|\bmod 192\neq 0\vee(\exists j.\ a_{\mathrm{j}}=\varnothing\vee b_{\mathrm{j}}=\varnothing))\\
k &=& \dfrac{|I_{\mathbf{d}}|}{192} \\
g_{\mathrm{r}}&=& 60000k + 40000 \\
\mathbf o[0..31]&\equiv&\begin{cases}
0x0000000000000000000000000000000000000000000000000000000000000001&\text{if}\ v\wedge\neg F\\
0x0000000000000000000000000000000000000000000000000000000000000000&\text{if}\ \neg v\wedge\neg F
\end{cases}\\
v&\equiv&(\log_{P_1}(a_1)\times\log_{P_2}(b_1)+\cdots+\log_{P_1}(a_{\mathrm{k}})\times\log_{P_2}(b_{\mathrm{k}})\equiv 1\mod q)\\
a_1&\equiv&\delta_1(I_{\mathbf d}[0..63])\\
b_1&\equiv&\delta_2(I_{\mathbf d}[64..191])\\\nonumber
\vdots\\
a_{\mathrm{k}}&\equiv&\delta_1(I_{\mathbf d}[(|I_{\mathbf d}|-192)..(|I_{\mathbf d}|-129)])\\
b_{\mathrm{k}}&\equiv&\delta_2(I_{\mathbf d}[(|I_{\mathbf d}|-128)..(|I_{\mathbf d}|-1)])
\end{eqnarray}

We define a precompiled contract for addition on $G_1$.

\begin{eqnarray}
\Xi_{\mathtt{BN\_ADD}}&\equiv&\Xi_{\mathtt{BN\_PRE}}\quad\text{except:}\\
\Xi_{\mathtt{BN\_ADD}}(\boldsymbol\sigma,g,I)&=&(\varnothing,0,A^0,())\quad\text{if}\ x=\varnothing\vee y=\varnothing\\
g_{\mathrm{r}} &=& 500\\
\mathbf o&\equiv&\delta_1^{-1}(x+y)\quad\text{where $+$ is the group operation in $G_1$}\\
x&\equiv&\delta_1(\bar I_{\mathbf d}[0..63])\\
y&\equiv&\delta_1(\bar I_{\mathbf d}[64..127])\\
\label{eq:complemented_input}\bar I_{\mathbf d}[x]&\equiv&\begin{cases}
I_{\mathbf d}[x]&\text{if}\ x < |I_{\mathbf d}|\\
0&\text{otherwise}
\end{cases}
\end{eqnarray}

@@

We assume the existence of functions $\mathtt{\small ECDSASIGN}$, $\mathtt{\small ECDSARECOVER}$ and $\mathtt{\small ECDSAPUBKEY}$. These are formally defined in the literature.
\begin{eqnarray}
\mathtt{\small ECDSAPUBKEY}(p_{\mathrm{r}} \in \mathbb{B}_{32}) & \equiv & p_{\mathrm{u}} \in \mathbb{B}_{64} \\
\linkdest{ECDSASIGN}{}\mathtt{\small ECDSASIGN}(e \in \mathbb{B}_{32}, p_{\mathrm{r}} \in \mathbb{B}_{32}) & \equiv & (v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) \\
\mathtt{\small ECDSARECOVER}(e \in \mathbb{B}_{32}, v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) & \equiv & p_{\mathrm{u}} \in \mathbb{B}_{64}
\end{eqnarray}
